Racial and Ethnic Differences in ETI: Outcomes

### 2024-08-05 Kamyron Jordan/Racial and Ethnic Differences in ETI/racial_and_ethnic_differences_in_eti_outcomes.qmd
removed LOESS again

# LOESS-smoothed outcome plots

```{r functions}
# Plots
loess_plot <- function(data = encounter, outcome, facet = F) {
  p <- ggplot(data, aes(x = Days, y = !!sym(outcome), color = Race)) +
    geom_point(
      shape = ".", aes(x = Days, y = !!sym(outcome)), inherit.aes = F,
      alpha = 0.1
    ) +
    geom_smooth(method = "loess", se = F) +
    theme_classic()
  if (facet) {
    p <- p + facet_wrap(~Race)
  }
  return(p)
}
```

```{r}
invisible(lapply(continuous_outcomes, function(o) {
  cat("\n")
  cat("\n")
  cat("##", o)
  cat("\n")
  cat("\n")
  print(loess_plot(outcome = o))
}))
```

@@

```{r results='asis'}
invisible(lapply(continuous_outcomes, function(o) {
  # Formula
  f <-
    as.formula(paste0(
      o,
      "~ bs(Days, knots = 0, degree = 1) * Race + (1 | eDWID)"
    ))
  m <- lmer(f, data = encounter)
  # Print table
  m %>%
    tbl_regression() %>%
    print()
  # Plot
  predict_response(m, terms = c("Days[-1095,0,730]", "Race")) %>% 
    plot()
}))
```

>>>>

@@

```{r results='asis'}
invisible(lapply(continuous_outcomes, function(o) {
  # Formula
  f <-
    as.formula(paste0(
      o,
      "~ bs(Days, knots = 0, degree = 1) * Race + (1 | eDWID)"
    ))
  m <- lmer(f, data = encounter)
  # Print table
  cat("\n")
  cat("##",o)
  cat("\n")
  cat("\n")
  cat("### Model results")
  cat("\n")
  m %>%
    tbl_regression() %>%
    print()
  cat("\n")
  # Plot
  cat("\n")
  cat("### Plot")
  cat("\n")
  predict_response(m, terms = c("Days[-1095,0,730]", "Race")) %>% 
    plot() %>%
    print()
  cat("\n")
}))
```
